A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-10-04 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
edited table, noticed agent and model were not cur

\newpage
\begin{table}[htbp]
    \caption{Node Agent}
    \begin{center}
    \begin{tabular}{|c|c|}
    \cline{1-2} 
    \textbf{Key Attributes}&{\textbf{Node Agent}} \\
    \cline{1-2} 
    \hline
    Connection Delay & Delay between when a node is created and when it can join the network \\
    Ticket List & List of random numbers used to pick the node for participation in a group\\
    Connection Failure Percent & Likelihood of disconnecting from the network\\
    Death Percent & Likelihood of going offline and never re-connecting\\
    Malicousness & determines if a node is considered malicous based on if the operator is malicious\\
    Operator  & the entity that runs this node\\
    \hline
    \textbf{ }&\textbf{Group Agent} \\
    \multicolumn{2}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
    \end{tabular}
    \label{table}
    \end{center}
    \end{table}

>>>>

\newpage
\begin{table}[htbp]
    \caption{Node Agent}
    \begin{center}
    \begin{tabular}{|c|c|}
    \cline{1-2} 
    \textbf{Key Attributes}&{\textbf{Node Agent}} \\
    \cline{1-2} 
    \hline
    Connection Delay & Delay between when a node is created and when it can join the network \\
    Ticket List & List of random numbers used to pick the node for participation in a group\\
    Connection Failure Percent & Likelihood of disconnecting from the network\\
    Death Percent & Likelihood of going offline and never re-connecting\\
    Malicousness & determines if a node is considered malicous based on if the operator is malicious\\
    Operator  & the entity that runs this node\\
    \hline
    \textbf{ }&\textbf{Group Agent} \\
    \hline
    Members & list of nodes that are members of the group. Nodes can repeat \\
    Expiry & number of blocks before group expires\\
    Malicious Percent & percentage of the groups members that are malicious\\
    Offline Percent & percentage of the groups members that are offline\\
    DKG Delay & User set delay simulating the distributed key generation process during group creation\\
    \hline
    \textbf{ }&\textbf{Signature Agent} \\
    \hline
    Group & list of nodes that are members of the group. Nodes can repeat \\
    Expiry & number of blocks before group expires\\
    Delay &  user specified time between being triggered and being published on chain\\
    Offline Percent & percentage of the groups members that are offline at the time of the signature\\
    Lynchpin operator percent & percent of the group owned by a single operator\\
    \hline
    \multicolumn{2}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
    \end{tabular}
    \label{table}
    \end{center}
    \end{table}
